Clustering in a hyperbolic model of complex networks.

### 2020-05-04 clustering_infinite_model.tex
Corrections to Lemma D 4.1 by Markus

\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}

@@

For any fixed value $y_0>0$, the set of points inside $\BallPo{y_0}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{y_0}}$. As $\mu(\BallPo{y_0}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by first picking $N \isd \Po( \mu(y_0) )$ and then taking $N$ i.i.d.~points in $\BallPo{y_0}$ according to the probability density $f \cdot 1_{\BallPo{y_0}} / \mu(y_0)$. (That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{y_0}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{y_0}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{y_0}$ chosen according to the mentioned re-normalized probability density function. This shows that, for every $k\geq 2$:
\[
	\CExp{C}{D=k, y=y_0} 
	= \frac{1}{\binom{k}{2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
	= \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\]
where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{y_0}$ with the above mentioned density.
Note that this does not depend on the value of $k$. For notational convenience, we will write 
\begin{equation}\label{eq:def_Py}
	P(y_0) := \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\end{equation}
with $u_1, u_2$ as above.

@@

\subsubsection{Explicit expressions for \texorpdfstring{$\gamma, \gamma(k)$}{gamma, gamma(k)} when \texorpdfstring{$\alpha=1$}{alpha equals 1}.}\label{ssec:alphais1}

We've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completeness. Since the rest of our 
proofs do not the depend on it the reader could decide to skip this section on a first reading.

Recall that $\Gamma^\ast(q,z) = \Gamma^+(q+1,z) + \Gamma^+(q,z)$. We will prove the following.

\begin{proposition}\label{prop:gammaais1}
If $\alpha=1$ then 
\begin{align*} 
\gamma &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
 	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
 	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
 \end{align*}
and
\begin{align*}
 \gamma(k) &= \frac{9 \eta^3}{2 k!} \Gamma^+(k-3,\eta)-\frac{\xi^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
 	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
 	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
 \end{align*}
with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm 
function.
\end{proposition}

Naturally, the proof proceeds by proving the analogue of Lemma~\ref{lem:Paneq1}:

\begin{lemma}\label{lem:Pais1}
If $\alpha = 1$, then
	\begin{align*}
	&P(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
e^{-y}  + 
\frac{1}{2}e^{-y}\Li_2(e^{-y})
	\end{align*}
	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dilogarithm function.
\end{lemma}

\begin{proof}
We want to compute the limit $\lim_{\alpha \rightarrow 1} P_\alpha(y_0(z_0))$. For $\alpha \neq 1$, we label the terms as follows:
%\begin{align*}
%&P_\alpha(y_0(z_0)) \\
%&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+s_3(\alpha,z_0)+s_4(\alpha,z_0) 
%+s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
%\end{align*}
\begin{align*}
&P_\alpha(y_0(z_0)) \\
&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+\frac{1}{\alpha-1}(s_3(\alpha,z_0)+s_4(\alpha,z_0)) 
+s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
\end{align*}
where
\begin{align*}
s_1(\alpha,z_0) &= -\frac{1}{8 \alpha}\\
s_2(\alpha,z_0) &= (\alpha-1/2)z_0 \\
s_3(\alpha,z_0) &= - \frac{(\alpha - 1/2)^2 z_0^2}{4}\\
s_4(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha}\\
s_5(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha}\\
s_6(\alpha,z_0) &= \frac{(1 - z_0)^{2 \alpha}}{8 \alpha} \\
s_7(\alpha,z_0) &= - \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4}
\end{align*}
Now, we consider the functions $s_i(\alpha) = s_i(\alpha,z_0)$ as functions of $\alpha$ only and compute their Taylor 
expansion at $\alpha=1$, for $i\in \{1,2,5,6,7\}$ up to linear and for $i\in \{3,4\}$ up to quadratic order, i.e. we 
write $s_i(\alpha) = s_i(1)+s_i'(1)(\alpha-1)+o(\alpha-1)$ for $i\in \{1,2,5,6,7\}$ and 
$s_i(\alpha)=s_i(1)+s_i'(1)(\alpha-1)+\frac{s_i''(1)}{2}(\alpha-1)^2+o((\alpha-1)^2)$ for $i\in \{3,4\}$. Using these expansions, we can rewrite
%\begin{align*}
%&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
%s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
%&\left.+\frac{1}{\alpha-1}(s_3(1)+s_4(1)+(s_3'(1)+s_4'(1))(\alpha-1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1)^2 +o((\alpha-1)^2)) \right)
%\end{align*}
\begin{align*}
&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
&\left.+\frac{s_3(1)+s_4(1)}{\alpha-1} + s_3'(1)+s_4'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1) +o((\alpha-1)) \right)
\end{align*}
In order to continue, we compute:
\begin{align*}
s_1(\alpha) &=-\frac{1}{8}+\frac{1}{8}(\alpha-1)+o(\alpha-1) \\
s_2(\alpha) &=\frac{1}{2}z_0 +z_0 (\alpha-1)+o(\alpha-1) \\
%s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{2}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
%s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
%&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
&\qquad+\frac{z_0^2}{8}\left(8\left(\ln\frac{z_0}{2}\right)^2+2\ln\frac{z_0}{2} - \frac{1}{2}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
s_5(\alpha) &= \frac{z_0^2}{4} B^-(1/2;3,0) +o(\alpha-1) \\
	&\hspace{10pt}+ z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) +1/2\int_0^{\frac{1}{2}} \ln(t(1-t))t^2(1-t)^{-1} \dd t \right)  (\alpha-1)+o (\alpha-1)\\
s_6(\alpha) &= \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1 + \smallO{a-1})\\
%s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
%&\qquad \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+o(\alpha-1)
s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) +o(\alpha-1) \\
	&\hspace{10pt}- z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) 
		+\int_0^{1-z_0} t(1-t)^{-2}\ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} \dd t \right) (\alpha-1).
\end{align*}
Based on this we see that
\begin{align*}
s_3(1)+s_4(1)=-\frac{1}{16}z_0^2+\frac{1}{16}z_0^2 =0
\end{align*}
and
\begin{align*}
&\sum_{i\in \{1,2,5,6,7\}} s_i(1) + s_3'(1)+s_4'(1) \\
&= -\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) 
+\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\left(\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2\right) 
+\left(-\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2\right) \\ 
&\hspace{50pt}+\left(\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}\right)+\left(\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0\right) &=0,
\end{align*}
using that %$B^-(\frac{1}{2};3,0)=-\frac{5}{8}+\ln 2$ and $B^-(1-z_0;2,-1)=-1+z_0^{-1}+\ln z_0$.
\begin{align*}
B^-(\frac{1}{2};3,0)&=\int_0^\frac{1}{2}t^2(1-t)^-1dt=\int_\frac{1}{2}^1 (1-s)^2 s^{-1}ds\\
&=\int_\frac{1}{2}^1 s^{-1}-2+sds = -2+\frac{1}{2}-\ln\frac{1}{2}+1-\frac{1}{8}=-\frac{5}{8}+\ln 2
\end{align*}
and
\begin{align*}
B^-(1-z_0;2,-1)&=\int_0^{1-z_0} t(1-t)^{-2}dt = \int_{z_0}^1 (1-s)s^{-2}ds \\
&=\int_{z_0}^1 s^{-2}-s^{-1}ds = -1+z_0^{-1}+\ln z_0.
\end{align*}

Finally, it follows that as $\alpha \to 1$,
\begin{align*}
P(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)
\end{align*}
Therefore, the desired value of $\lim_{\alpha \rightarrow 1} P(y_0(z_0))$ is given by
\begin{align*}
&\sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))\\
	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) 
		+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
	&\hspace{10pt}+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+ \frac{1}{2}\int_0^{\frac{1}{2}} 
		\ln(t(1-t)) \, t^2(1-t)^{-1} \dd t \right) \\
	&\hspace{10pt}- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0}\ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} 
		\dd t \right) \\
	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2
		+\frac{z_0^2}{8}\ln\frac{z_0}{2} - \frac{z_0^2}{32} \\
	&\hspace{10pt}-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32} +\frac{z_0^2 \ln2}{4}\\
	&\hspace{10pt}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t(1-t)) \, t^2(1-t)^{-1}\dd t \\
	&\hspace{10pt}+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
	&\hspace{10pt}+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2
		-z_0^2\int_0^{1-z_0} \ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2}  \dd t \\
	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2\int_0^{\frac{1}{2}} \ln(t(1-t)) \, t^2(1-t)^{-1} \dd t \\
	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} \ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} \dd t \\
	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)) \\
	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2+z_0(1 + \frac{1}{2}(2-z_0) \ln(z_0) 
		+ \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) \\
	&\hspace{10pt}+\frac{1}{2}z_0 \Li_2(z_0)) - z_0^2   -\frac{1}{2}  z_0^2\Li_2(1) \\
	&=\frac{9}{4}z_0-\frac{25}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
	&\hspace{10pt}-\frac{1}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 \\
	&\hspace{10pt}- \Li_2(1/2)-\Li_2(1)+\Li_2(z_0)) -\frac{1}{2}z_0^2(\ln z_0)^2 - \frac{1}{2} z_0(1-z_0) \ln(1-z_0)
\end{align*}
where we used that
\begin{align*}
	z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1} \dd t
	&= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2),
\end{align*}
and
\begin{align*}
	&z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2} \dd t\\
	&= -\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 \Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1).
\end{align*}
By expanding the squares and collecting terms, the last expression can be simplified to
\begin{align*}
&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) + 
z_0^2 \left(-7/8 - \frac{\ln(2)^2+2\Li_2(1/2) + 2\Li_2(1)}{4} \right) + 
\frac{1}{2}z_0^2 \Li_2(z) \\
=&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
z_0^2  + 
\frac{1}{2}z_0^2 \Li_2(z)
\end{align*}
which finishes the computation.
\end{proof}

\begin{proofof}{Proposition~\ref{prop:gammaais1}}
It suffices to find the value of $J$ and $I^{(k)}$ 
at $\alpha = 1$. We can do this by computing the integrals with the expression for $P(y)$ that we found for $\alpha=1$, i.e.
\begin{align*}
	J &= 2\alpha\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) - \frac{7+\pi^2}{8}
		z^2  + \frac{1}{2}z^2 \Li_2(z)\right) z^{2\alpha -1} \dd z \\
	&=\frac{575-12\pi^2}{576}
\end{align*}
and 
\begin{align*}
	I^{(k)} &= \frac{2\alpha \xi^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
		- \frac{7+\pi^2}{8}	z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{2\alpha-k-1} e^{-\xi/z} \dd z \\
	&= \frac{2 \eta^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
		- \frac{7+\pi^2}{8} z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{1-k} e^{-\eta/z} \dd z \\
	&= \frac{9 \eta^k}{2 k!}\eta^{3-k}\Gamma^+(k-3,\eta)-\frac{\eta^k}{k!}\frac{7+\pi^2}{4}\eta^{4-k}\Gamma^+(k-4,\eta)\\
	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}dz+\frac{\eta^k}{k!}\int_0^1 z^{3-k} 
		\Li_2(z) e^{-\eta/z} \dd z \\
	&=\frac{9 \eta^3}{2 k!}\Gamma^+(k-3,\eta)-\frac{\eta^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}dz+\frac{\eta^k}{k!}\int_0^1 z^{3-k} 
		\Li_2(z) e^{-\eta/z} \dd z
\end{align*}
where $\eta = \frac{4\nu}{\pi}$ and and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function. 
Plugging this into ~\eqref{eq:gammaint} and~\eqref{eq:gammakint} yields the expressions in the statement of the proposition.
\end{proofof}

>>>>

\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{-\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}

@@

For any fixed value $y_0>0$, the set of points inside $\BallPo{y_0}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{y_0}}$. As $\mu(\BallPo{y_0}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by first picking $N \isd \Po( \mu(y_0) )$ and then taking $N$ i.i.d.~points in $\BallPo{y_0}$ according to the probability density $f \cdot 1_{\BallPo{y_0}} / \mu(y_0)$. (That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{y_0}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{y_0}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{y_0}$ chosen according to the mentioned re-normalized probability density function. This shows that, for every $k\geq 2$:
\[
	\CExp{C}{D=k, y=y_0} 
	= \frac{1}{\binom{k}{2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
	= \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\]
where $u_1,\dots, u_k$ are i.i.d.~points in $\BallPo{y_0}$ with the above mentioned density.
Note that this does not depend on the value of $k$. For notational convenience, we will write 
\begin{equation}\label{eq:def_Py}
	P(y_0) := \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\end{equation}
with $u_1, u_2$ as above.

@@

### 2020-05-04 introduction.tex
Corrections to Lemma D 4.1 by Markus

For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in 
probability to $X$, and we write $X_n \xrightarrow[n\to\infty]{L_1} X$ if $X_n$ converges to $X$ in the $L_1$ sense 
(i.e.~if $\Ee |X_n-X| \to 0$.)

@@

$$ \frac{c(k_n;G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L_1} 1. $$

@@

\noindent
The conclusion of Theorem~\ref{thm:mainktoinfty} is slightly stronger than $c(k_n; G_n)/\gamma(k_n) 
\xrightarrow[n\to\infty]{\Pee} 1$, which might alternatively be written as $c(k_n;G_n) = (1+o(1)) \gamma(k_n)$ a.a.s., using notation that is common in the random graphs community.

@@

\subsubsection{Uniform convergence.}

Our results for the local clustering function in fact imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ 
where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. 
To see this we first observe that for {\em fixed} $k$, the statement $c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k)$
is equivalent to $c(k;G_n)/\gamma(k) \xrightarrow[n\to\infty]{L_1} 1$.
Now let
\[
	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|}.
\]
Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainkfixed} and Theorem~\ref{thm:mainktoinfty}
\[
	\lim_{n \to \infty} \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|} 
	= \lim_{n \to \infty}\Exp{\left|\frac{c(b_n; G_n)}{\gamma(b_n)} - 1\right|} = 0.
\]

>>>>

For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in 
probability to $X$. %, and we write $X_n \xrightarrow[n\to\infty]{L_1} X$ if $X_n$ converges to $X$ in the $L_1$ sense (i.e.~if $\Ee |X_n-X| \to 0$.)

@@

$$ \frac{c(k_n;G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{\Pee} 1. $$

@@

\noindent
The statement of Theorem~\ref{thm:mainktoinfty} is equivalent to $c(k_n;G_n) = (1+o(1)) \gamma(k_n)$ a.a.s., using notation that is common in the random graphs community. %$c(k_n; G_n)/\gamma(k_n)\xrightarrow[n\to\infty]{\Pee} 1$, which might alternatively be written as

@@

%\subsubsection{Uniform convergence.}

%Our results for the local clustering function in fact imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ 
%where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. 
%To see this we first observe that for {\em fixed} $k$, the statement $c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k)$
%is equivalent to $c(k;G_n)/\gamma(k) \xrightarrow[n\to\infty]{L_1} 1$.
%Now let
%\[
%	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|}.
%\]
%Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainkfixed} and Theorem~\ref{thm:mainktoinfty}
%\[
%	\lim_{n \to \infty} \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|} 
%	= \lim_{n \to \infty}\Exp{\left|\frac{c(b_n; G_n)}{\gamma(b_n)} - 1\right|} = 0.
%\]
